\section{Review of \acs*{cad} sytems for \ac{cap}}\label{chap:3}
\graphicspath{{3_review/figures/}}

\input{2_modality/fig-1-cad-framework.tex}

As previously mentioned \acs{sec}\,\ref{sec:intro:cad}, \acp{cad} are developed
to advise and backup radiologists in their tasks of \ac{cap} detection and
diagnosis, but not to provide fully automatic decisions~\cite{Giger2008}.
\acp{cad} can be divided into two different sub-groups: either as \ac{cade},
with the purpose to highlight probable lesions in \ac{mri} images, or
\ac{cadx}, which focuses on differentiating malignant from non-malignant
tumours~\cite{Giger2008}.
Moreover, an intuitive approach, motivated by developing a framework combining
detection-diagnosis, is to mix both \ac{cade} and \ac{cadx} by using the output
of the former mentioned as a input of the latter named.
Although the outcomes of these two systems should differ, the framework of both
\ac{cad} systems is similar.
A general \ac{cad} work-flow is presented in \acs{fig}\,\ref{fig:wkfcad}.

\ac{mri} modalities mentioned in \acs{chp}\,\ref{chap:2} are used as inputs of
\ac{cad} for \ac{cap}.
These images acquired from the different modalities show a large variability
between patients: the prostate organ can be located at different positions in
images --- due to patient motion, variation of acquisition plan --- and the
\ac{si} can be corrupted with noise or artifacts during the acquisition process
caused by the magnetic field non-homogeneity or the use of endorectal coil.
To address these issues, the first stage of \ac{cad} is to pre-process
\ac{mpmri} images to reduce noise, remove artifacts, and standardize the
\ac{si}.
Subsequently, most of the later processes are only focusing on the prostate
organ; therefore it is necessary to segment the prostate in each \ac{mri}
modality to define it as a \ac{roi}.
However, data may suffer from misalignment due to patient motions or different
acquisition parameters.
Therefore, a registration step is usually performed so that all the previously
segmented \ac{mri} images are in the same reference frame.
Registration and segmentation can be swapped depending on the strategy chosen.

Some studies do not fully apply the methodology depicted in
\acs{fig}\,\ref{fig:wkfcad}.
Details about those can be found in \acs{tab}~\ref{tab:sumpap}.
Some studies bypass the pre-processing stages to proof the robustness of their
approaches to noise or other artifacts, by using directly the raw data as
inputs of their \ac{cad} systems.
In some cases, prostate segmentation is performed manually as well as
registration.
Sometimes, it is also assumed that no patient motions occur during the
acquisition, removing the need of registering the \ac{mpmri} images.

Once the data are regularized, it becomes possible to extract features and
classify the data to obtain the location of possible lesions (i.e.,
\ac{cade}) or/and the malignancy nature of these lesions (i.e., \ac{cadx}).

In \iac{cade} framework, \textit{possible lesions are segmented automatically}
and further used as input of \iac{cadx}.
Nevertheless, some works also used a fusion of \ac{cade}-\ac{cadx} framework in
which a voxel-based features are directly used, in which the location of the
malignant lesions are obtained as results.
On the other hand, manual lesions segmentation is not considered to be part of
\ac{cade}.

\Ac{cadx} is composed of the processes allowing to \textit{distinguish
  malignant from non-malignant tumours}.
Here, \ac{cap} malignancy is defined using the grade of the \ac{gs} determined
after post biopsy or prostatectomy.
As presented in \ac{fig}\,\ref{fig:wkfcad}, \ac{cadx} is usually composed of
the three common steps used in a classification framework: (i) features
detection, (ii) feature extraction/selection, and (iii) feature
classification.

This chapter is organized using the methodology presented in
\acs{fig}\,\ref{fig:wkfcad}.
Methods embedded in the image regularization framework are presented initially
to subsequently focus on the image classification framework, being divided into
\ac{cade} and \ac{cadx}.
Finally, we present a summary of the results reported in the state-of-the-art
as well as a discussion that follows.
\Acl{tab}~\ref{tab:sumpap} summarizes the 56 different \ac{cad} studies
reviewed in this section.
The first set of information reported is linked to the data acquisition such as
the number of patients included in the study, the modalities acquired as well
as the strength of the field of the scanner used.
Subsequently, information about the prostate zones considered in the \ac{cad}
analysis --- i.e. \ac{pz} or \ac{cg} --- are reported since that detecting
\ac{cap} in the \ac{cg} is a more challenging problem and has received
particular attention only in the recent publications.

The papers have been selected by investigating referenced international
peer-reviewed journals as well as international peer-reviewed conferences.
Additionally, a breadth-search first (or snowball sampling) have been used to
refine missing publications.
Only studies proposing \ac{cad} systems specifically for \ac{cap} have been
reviewed.

\input{3_review/Table-survey.tex}
\input{3_review/image-regularization.tex}
\input{3_review/image-classification.tex}
\input{3_review/discussion.tex}
